Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-06-12 03_Prep_data.Rmd
Correct clustering code

```{r simple_clusters}
slim_PM_dat <- slim_PM_dat %>%
   mutate(
      spray_management = case_when(
         fungicide_timing_1 < 0 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Early",
         fungicide_timing_1 >= 0 &
            fungicide_timing_1 < 4 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Recommended",
         fungicide_timing_1 >= 4 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Late",
         fungicide_timing_1 < 0 &
            !is.na(fungicide_application_2) ~ "Early_plus",
         fungicide_timing_1 >= 0 &
            fungicide_timing_1 < 4 &
            !is.na(fungicide_application_2) ~ "Recommended_plus",
         fungicide_timing_1 >= 4 ~ "Late_plus",
         TRUE ~ "Other"
      )
   )

@@

```{r simpler_clusters_REMOVE}
slimmer_PM_dat <-
   slim_PM_dat[slim_PM_dat$spray_management != "Late" &
                  slim_PM_dat$spray_management != "Early_plus", ]

>>>>

```{r simple_clusters}
slim_PM_dat <- slim_PM_dat %>%
   mutate(
      spray_management = case_when(
         fungicide_timing_1 < 0 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Early",
         fungicide_timing_1 >= 0 &
            fungicide_timing_1 < 4 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Recommended",
         fungicide_timing_1 >= 4 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Late",
         fungicide_timing_1 < 0 &
            !is.na(fungicide_application_2) ~ "Early_plus",
         fungicide_timing_1 >= 0 &
            fungicide_timing_1 < 4 &
            !is.na(fungicide_application_2) ~ "Recommended_plus",
         fungicide_timing_1 >= 4 &
            !is.na(fungicide_application_2) ~ "Late_plus",
         TRUE ~ "Other"
      )
   )

@@

```{r simpler_clusters_REMOVE}
slimmer_PM_dat <-
   slim_PM_dat[#slim_PM_dat$spray_management != "Late" &
                  slim_PM_dat$spray_management != "Early_plus", ]
